---
title: "Vignette"
author: "Silvia Girlanda"
date: "2024-05-16"
output: html_document
---

# My first Markdown file!

This file contains functions for R scripting in Geo-Ecological Remote Sensing.

We are going to make use of the following packages:

```{r}
library(imageRy)
library(terra)
library(viridis)
```

In order to visualize the list of data use:
```{r, eval=T}
im.list()
```

In order to import data we can use the following function:
```{r, eval=T}
mato<-im.import("matogrosso_l5_1992219_lrg.jpg")
```

This plot is related to the following bands: band 1 = NIR, band 2 = red, band 3 = green.

We are using a set from Mato Grosso, and we can plot it in a RGB space, as:
```{r, eval=T}
im.plotRGB(mato,1,2,3)
```

We can change the visualization by changing bands in the RGB space, as:
```{r, eval=T}
im.plotRGB(mato,2,1,3)
```

In order to look different bands combintaions altogheter we can use:
```{r, eval=T}
par(mfrow=c(1,3))
im.plotRGB(mato,1,2,3)
im.plotRGB(mato,2,1,3)
im.plotRGB(mato,3,2,1)
```

## Calculating spectral indices:
```{r, eval=T}
dvi <- mato[[1]]-mato[[2]]
viridisc <- colorRampPalette(viridis(7))(255)
plot(dvi, col=viridisc)
```

## Calculating variability:
```{r, eval=T}
sd5 <- focal(mato[[1]], matrix(1/25, 5, 5), fun=sd)
plot(sd5, col=magma(100))
```
